\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-08 paper/paper.tex
Prepend to intro, fix typo in model compare

\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
We present an approach to modeling failure data with heavy censoring, multiple censoring and multiple truncation. We extend the generalized limited failure population model (GFLP) of Chan and Meeker which provides a generative model for failure distributions characterized by a "bathtub" hazard function (citation). This model provides an adequate fit to failures of complex systems by differentiating between early and late types of failures as well as the propensity toward early failure. We discuss the case where the data are grouped, suggesting that we might expand the model, accounting for differences among groups. We show that by modeling the data hierarchically, we can deal with groups of various sample sizes by borrowing information across groups. We illustrate our approach on a large set of failure data for hard disk drives made available by the hard drive backup company, Backblaze (citation).

@@

In addition to graphically examining model fits via posterior credible bands, we compared the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  The predictive accuracy from a fitted Bayesian model can be estimated simply with posterior simulations of the model parameters \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior parameters with the $i$th data point removed.  The final expected point-wise predictive density is the sum over all observations (elpd $=\sum{\logp(y_i|y_{-i}$)}).  To obtain a more stable estimate of elpd, Vehtari et. al suggest using Pareto smoothed importance weights (PSIS) since the tail of the importance weights used to estimate elpd is often long.  We computed the elpd for all 4 models using the R package loo \cite{loopackage}.  When $n$ is large, the distribution of the elpd is approximately normal and models can be statistically compared.  We calculated the difference in expected predictive accuracy for all 4 models as well as the standard error of the difference.  As the model complexity increased, the predictive accuracy improved (Table 1).  Of all the models, Model 4 had the best predictive accuracy and was significantly better than models 1-3.

>>>>

\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
Failure data for series systems may be collected at the system level by end-users interested only in the lifetime of the system. In the case of complex, high-reliability systems where cause of failure is not available, a model of failure which
\begin{enumerate}[a]
\item can be estimated from the observed data
\item is flexible enough to fit the observed data
\item relies on an approximation of the understood underlying process
\end{enumerate}
is desireable. We present a Bayesian, hierarchical modeling approach for grouped failure data. We demonstrate this approach with a large, heavily censored real data set with multiple right-censoring and left truncation times. We extend the generalized limited failure population model (GLFP) by \citet{chan}, which provides a generative model for failure times in a population with infant mortality. This model is an example of a bathtub distribution, exhibiting distinct early and late failure modes. The GLFP model assumes there are two causes of failure, one of which affects only a fraction of the population, and that the cause of failure is unobserved. We extend this model to grouped data and show that by borrowing information across groups we can acheieve good model fits for almost all groups. By working with posterior samples, we can easily make inference on a wide range of quantities of interest while accounting for uncertainty.

@@

In addition to graphically examining model fits via posterior credible bands, we compared the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  The predictive accuracy from a fitted Bayesian model can be estimated simply with posterior simulations of the model parameters \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior parameters with the $i$th data point removed.  The final expected point-wise predictive density is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  To obtain a more stable estimate of elpd, Vehtari et. al suggest using Pareto smoothed importance weights (PSIS) since the tail of the importance weights used to estimate elpd is often long.  We computed the elpd for all 4 models using the R package loo \cite{loopackage}.  When $n$ is large, the distribution of the elpd is approximately normal and models can be statistically compared.  We calculated the difference in expected predictive accuracy for all 4 models as well as the standard error of the difference.  As the model complexity increased, the predictive accuracy improved (Table 1).  Of all the models, Model 4 had the best predictive accuracy and was significantly better than models 1-3.
